Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-01 PaperVictor.tex
Highlight new changes

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers,sort&compress]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
%\usepackage{cite}
\usepackage{braket}
\usepackage{bm}
\usepackage{xcolor}
\newcommand{\hl}[1]{{\color{blue}#1}}
\begin{document}
\bibliographystyle{unsrt}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\shortauthors{V. Castillo-Gallardo et~al.}

@@

\begin{abstract}
We design, optimize, fabricate, and characterize highly
reflective quasi-omnidirectional multilayered structures with a wide
angular and spectral range. We consider chirped structures with layers
of gradually varying thicknesses and structures made by stacking
Bragg-type sub-structures, and we maximized their numerically calculated
reflectance averaged over different spectral ranges keeping a minimum
thickness for given pairs of refractive indices. We fabricated some of
these structures with porous silicon with a low refractive contrast
between adjacent layers,
and compared their measured  optical properties to the theoretical
results and to previous works. We obtained relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges that compare favorably to others reported in the
literature.

@@

We developed a formalism to design and optimize highly
reflective quasi-omnidirectional multilayered mirrors with a wide
spectral range. We considered two kinds of systems, chirped structures with a gradual
change in layer thicknesses and
stacked Bragg mirrors tuned so that their bandwidths overlap, and
optimized their
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing a stabilized transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
at 1160 nm and 1925 nm respectively were shown. In addition,
we fabricated a stacked structure  with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges that compare favorably to those in
the literature.
We believe that our analysis techniques can
be used for the optimization of the reflectance not only in
multilayered porous silicon systems but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

@@

\bibliography{Bibliografia}

>>>>

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers,sort&compress]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}
\usepackage{xcolor}
\newcommand{\hl}[1]{{\color{blue}#1}}
\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\shortauthors{V. Castillo-Gallardo et~al.}

@@

\begin{abstract}
\hl{We design, optimize, fabricate, and characterize highly
reflective quasi-omnidirectional multilayered structures with a wide
angular and spectral range. We consider chirped structures with layers
of gradually varying thicknesses and structures made by stacking
Bragg-type sub-structures, and we maximized their numerically calculated
reflectance averaged over different spectral ranges keeping a minimum
thickness for given pairs of refractive indices. We fabricated some of
these structures with porous silicon with a low refractive contrast
between adjacent layers,
and compared their measured  optical properties to the theoretical
results and to previous works. We obtained relatively thin
quasi-omnidirectional mirrors with wide bands over different
wavelength ranges that compare favorably to others reported in the
literature.}

@@

\hl{We developed a formalism to design and optimize highly
reflective quasi-omnidirectional multilayered mirrors with a wide
spectral range. We considered two kinds of systems, chirped structures with a gradual
change in layer thicknesses and
stacked Bragg mirrors tuned so that their bandwidths overlap, and
optimized their}
reflectance with minimum thickness for a given pair of refractive
indices. Numerical calculations were
carried out employing a stabilized transfer matrix method and we optimized the
design parameters to obtain maximal reflectance averaged over different spectral ranges for
all angles.
We fabricated some of the optimized structures with
porous silicon
dielectric multilayers with low refractive contrast and compared their measured  optical properties
with the calculations. Two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi-omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
\hl{at 1160 nm and 1925 nm respectively were shown. In addition,
we fabricated a stacked structure} with a
quasi-omnidirectional bandwidth of 1800 nm centered at 1850 nm and a
thickness of 41.5 $\mu$m, which is almost two thirds as thick as the chirped structure.
Thus, our techniques allowed us to obtain relatively thin
quasi-omnidirectional mirrors with wide bands
over different wavelength ranges \hl{that compare favorably to those in
the literature.
We believe that our analysis techniques can
be used for the optimization of the reflectance not only in
multilayered porous silicon systems but also for systems with other types of
materials with low refractive index contrast. The present study could
also be useful for obtaining omnidirectional dielectric mirrors in
large spectral regions using different materials,  flat focusing
reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with
a wide angular independent response.

@@

\bibliographystyle{unsrt}
\bibliography{Bibliografia}
